% Version 2006-12-05
\documentclass[12pt]{dalcsthesis}

% Algorithms
\usepackage{algorithmic}
\usepackage{algorithm}

\begin{document}

\mcs  % options are \mcs, \macs, \mec, \mhi, \phd, and \bcshon
\title{The title}
\author{Noah Body}
\defenceday{1}
\defencemonth{November}
\defenceyear{2006}
\convocation{May}{2007}

% Use multiple \supervisor commands for co-supervisors.
% Use one \reader command for each reader.

\supervisor{D. Prof}
\reader{D. Odaprof}
\reader{A. External}

\nolistoftables
\nolistoffigures

\frontmatter

\begin{abstract}
This is a test document.
\end{abstract}

\begin{acknowledgements}
Thanks to all the little people who make me look tall.
\end{acknowledgements}

\mainmatter

\chapter{Introduction}

Get it done!  Use reference material by Lamport~\cite{latex-by-lamport} or
Gooses, Mittelback, and Samarin~\cite{latex-companion}.

\chapter{Doing It}

\section{Getting Ready}

Get all the parts that I need.  I can throw in a whole pile of terms like
preparation,
methodology,
forethought,
and
analysis
as examples for me to use in the future.

\section{Next Step}

Do it!

Of course, you have to have pictures to show how you did it to make people
understand things better.

\begin{algorithm}

 \caption{Add Non Essential Views}
 \label{alg-add_non_essential_views}

 \begin{algorithmic}[1]

    \INPUT A tree $E$ consisting of the selected group-bys, and a
    guiding graph $G$. Also used are auxiliary variables $BP$
    (best plan) and $CP$ (current plan).

    \OUTPUT Reduced tree $R$.

    \COMMENT{Add nodes from $G - R$ to $E$ as long as the total
    cost improves}

    \REPEAT
        \STATE clear $BP$

        \FOR{every $v \: in \: G - R$}
            \STATE clear $CP$
            \STATE $CP.node = v$
            \STATE {\sf FindBestParent(R, CP)}
            \STATE {\sf FindBestChildren(R, CP)}

            \IF{ {\em CP.benefit\/} $>$ {\em BP.benefit\/} }
                \STATE $BP = CP$
            \ENDIF
        \ENDFOR

        \IF{ {\em BP.benefit\/} $> 0$}
            \STATE add $BP.node$ to $R$ and update $R$ accordingly
        \ENDIF

    \UNTIL{ {\em BP.benefit\/} $<= 0$}

 \end{algorithmic}
\end{algorithm}

Thanks to Todd Eavis for providing the sample algorithm.

\chapter{Conclusion}

Did it!

\bibliographystyle{plain}
\bibliography{simple}

\end{document}
